\LARGE \bf Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving

### 2016-01-12 paper1.tex
fleshed out each jerk profile

@@

For the purposes of this work, the objective of trajectory planning is to take a 2 dimensional (horizontal plane) path, and compute a series of constant jerk intervals for motion along the length of the path which is time optimal yet still falls within constraints on speed, acceleration, and jerk.
It is assumed that an independent path planner will produce this information.
Prescribed initial and end conditions for position, speed, and acceleration must also be honored. 
This means that the desired trajectory plan is one dimensional, so using curvilinear coordinates will significantly simplify the solution.

% Need some lead in here?

% \subsection{Simple Case}

Consider, as a starting point, the case in which a vehicle is at rest and needs to accelerate to some travelling speed, maintain that speed for some distance, then brake to a stop at a prescribed end location.
Figure \ref{fig:7phaseprofile} shows this trajectory over time.
The problem is defined by the vector of known values $\bf{G} = [v_i, v_f, L, v_m]$, being initial speed, final speed, the total distance, and the speed limit, respectively.
If the desired peak acceleration and jerk ($a_m$ and $j_m$, respectively) are known, then the profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, \Delta t_2, ..., \Delta t_M]$.
Jerk and peak acceleration may be different when reducing speed versus increasing speed to more closely mirror human driving behavior \emph{Citation}.
The user-defined parameters now become $\bar{a}_m = [a^+_m , a^-_m]$ and $\bar{j}_m = [j^+_m , j^-_m]$.
There are, however multiple solutions for $\Delta t_2$, $\Delta t_4$, and $\Delta t_6$.
The proper solution must be chosen by eliminating negative and complex solutions.

@@

It is obvious that there are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\bar{a}_m$ and $\bar{j}_m$.
The authors then propose that 4 other basic profiles be defined, and an algorithm constructed which judiciously chooses the appropriate profile for every segment defined by a vector $\bf{G}$.
The other profiles are explained below in section \ref{sec:jerkprofiles}.
A path is then a set of $i$ segments, each of which is defined by a set of parameters $G_i$ and can be solved indivually in sequence.
Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}.

@@

@@

>>>>

Paragraphs here

Paragraphs here

@@

For the purposes of this work, the objective of trajectory planning is to take a 2 dimensional (horizontal plane) path, and compute a series of constant jerk intervals for motion along the length of the path which is time optimal yet still falls within constraints on speed, acceleration, and jerk.
Integrating piecewise constant jerk over time yields acceleration which is piecewise linear over time, speed which is piecewise quadratic over time, and position which is piecewise cubic over time.
It is assumed that the path planner operates independently from the trajectory planner and tracker.
Prescribed initial and end conditions for position, speed, and acceleration must also be honored. 
This means that the desired trajectory plan is one dimensional, so using curvilinear coordinates will significantly simplify the solution.

% Need some lead in here?
% \subsection{Simple Case}

@@

Consider, as a starting point, the case in which a vehicle is at rest and needs to accelerate to some travelling speed, maintain that speed for some distance, then brake to a stop at a prescribed end location.
Figure \ref{fig:7phaseprofile} shows this trajectory over time.
The problem is defined by the vector of known values $\bar{G}  = [v_i, v_f, L, v_m]$, being initial speed, final speed, the total distance, and the speed limit, respectively.
If the desired peak acceleration and jerk ($a_m$ and $j_m$, respectively) are known, then the profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
Jerk and peak acceleration may be different when reducing speed versus increasing speed to more closely mirror human driving behavior \emph{Citation}.
The user-defined parameters now become $\bar{a}_m = [a^+_m , a^-_m]$ and $\bar{j}_m = [j^+_m , j^-_m]$.
There are, however, multiple solutions for $\Delta t_2$, $\Delta t_4$, and $\Delta t_6$.
The proper solution must be chosen by eliminating negative and complex solutions.

It is obvious that there are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\bar{a}_m$ and $\bar{j}_m$.
The authors then propose that 4 other basic profiles be defined, and an algorithm constructed which judiciously chooses the appropriate profile for every segment defined by a vector $\bf{G}$.
The other profiles are explained below in section \ref{sec:jerkprofiles}.
A path is then a set of $N$ segments, each of which is defined by a set of parameters $G_i, i = 1 ... N$ and can be solved indivually in sequence.
Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}.

@@

There are a total of five potential jerk profiles which have been created to cover all feasible values in $\bar{G}$. All impossible scenarios are automatically ruled out.

\subsubsection{6 Phase}
\label{sec:6phase}

The case mentioned above wherein the speed limit is too high for a solution to exist for a 7 phase profile. The middle travel period is removed, so that the vehicle increases speed and then immediately decreases speed. The peak speed in this case has a solution, but cannot be manipulated directly.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.6\columnwidth]{graphics/6phase_v(s).png}
  \caption{6 phase profile, displayed as speed vs. position along path}
  \label{fig:6phaseprofile}
\end{figure}

\subsubsection{4 Phase}
\label{sec:4phase}

When $v_i < v_m \simeq v_f$, the vehicle should increase speed, then maintain that speed for the distance remaining in the segment.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.6\columnwidth]{graphics/4phase_v(s).png}
  \caption{4 phase profile, displayed as speed vs. position along path.}
  \label{fig:4phaseprofile}
\end{figure}

\subsubsection{Reversed 4 Phase}
\label{sec:reversed4phase}

When $v_i \simeq v_m > v_f$, it would be nonsensical to immediately brake. The initial speed is maintained for a period before applying the brakes.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.6\columnwidth]{graphics/4Rphase_all_derivatives.png}
  \caption{Reversed 4 phase profile, displayed as speed vs. position along path.}
  \label{fig:4rphaseprofile}
\end{figure}

\subsubsection{3 Phase}
\label{sec:3phase}

A change from one speed to another. This presents a difficulty in that either $L$ or $v_f$ may be enforced, but not both (there is no solution to enforce both). As such, this profile is chosen for a segment in which it is impossible to completely arrive at the end speed given the initial speed.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.6\columnwidth]{graphics/3phase_v(s).png}
  \caption{3 phase profile, displayed as speed vs. position along path.}
  \label{fig:3phaseprofile}
\end{figure}

@@

% make sure to incorporate extensibility to other constraints
asdf
